Mergeable Types

### 2017-02-27 paper/related.tex
related work

>>>>

There have been numerous proposals over the years for realizing
distributed functionality in a functional programming context.
Poly/ML~\cite{Mat97} and Facile~\cite{TLK+93} both extend Standard ML
with distributed programming abstractions.  Kali-Scheme~\cite{CJK95}
defines a distributed extension for Scheme-48, and Cloud
Haskell~\cite{EBPJ11} describes a domain-specific language that
enables development of distributed Haskell programs.
Obliq~\cite{Car95} explores issues related to mobility, lexical
scoping, and network references in an object-oriented framework that
enables safe (i.e., lexical) transmission of closures.  However,
unlike \name, none of these systems consider issues of object
replication or consistency as central to their programming models.
The realities of modern-day scalable distributed systems, especially
those that are constructed from geographically distributed
participants, dictate that we must necessarily grapple with
consistency issues to achieve any kind of reasonable performance; it
is noteworthy that replication is inherent in many widely-used
distributed system implementations today (e.g.,
Cassandra~\cite{Cassandra} or Dynamo~\cite{Dynamo}), which provide
only weak consistency guarantees.  Rather than providing, as other
approaches have, a low-level operational treatment of replication, our
primary contribution is the development of a principled high-level
approach to framing issues of consistency and replication.  Our goal
is to leverage functional programming principles to minimize
disruption to the way programmers structure and reason about their
applications, without compromising efficiency or performance.  Indeed,
the semantics of mergeable types and versioning has utility in any
concurrent setting that must deal with non-trivial coordination and
synchronization costs, even without taking distribution or replication
issues into account.
